### 2016-10-07 oldmort.Rnw
add causes 41

%\usepackage[tablesonly]{endfloat}
\usepackage[figuresonly]{endfloat}

@@

For a detailed presentation we refer to \citet{segb16}. Her is a short
summary.

@@

>>>>

%\usepackage[tablesonly]{endfloat}
%\usepackage[figuresonly]{endfloat}
\usepackage{endfloat}

@@

For a detailed presentation we refer to \citet{segb16}. Here is a short
summary.

@@

\section{Results, causes 41 \ldots}

<<causes41>>=
load("data/vb.rda")
x <- substr(vb$ULORSAK, 1, 2)
vb$event <- vb$event & (!is.na(vb$ULORSAK)) & (x %in% "41")
vb$exposure <- with(vb, exit - enter)
vbTab <- aggregate(vb[, c("event", "exposure")], 
                   vb[, c("sex", "age", "period", "cohort", 
                          "urban", "civst", "hisclass")], 
                   FUN = sum)
vbTab$hisclass <- factor(vbTab$hisclass)
vbTab$age <- factor(vbTab$age)
@

<<41colorc>>=
## Colors for plotting strata:
scol <- c("blue", rep("darkgreen", 2), "red")
## Common for all groups:

%The distribution over time periods.
<<41getske4060>>=
cap1w <-  "Cumulative hazards for HISCLASS by time period, ages 40--64, women, causes 41."
scap1w <-  "Cumulative hazards, ages 40--64, women, causes 41."
cap1m <-  "Cumulative hazards for HISCLASS by time period, ages 40--64, men, causes 41."
scap1m <-  "Cumulative hazards, ages 40--64, men, causes 41."
##
cap12 <- "Total hazard of dying before age 60 for a 40 year old person by HISCLASS and decade, women (top) and men (bottom), causes 41."
scap12 <- "Total hazard by HISCLASS, ages 40--64, causes 41."    
cap12log <- "Total hazard of dying before age 60 for a 40 year old person by HISCLASS and decade, women (top) and men (bottom). The last decades, causes 41."
scap12log <- "Total hazard by HISCLASS, ages 40--64, last years, causes 41."

cap2w <-  "Cumulative hazards for HISCLASS by time period, ages 65--89, women, causes 41."
scap2w <-  "Cumulative hazards, ages 65--89, women, causes 41."
cap2m <-  "Cumulative hazards for HISCLASS by time period, ages 65--89, men, causes 41."
scap2m <-  "Cumulative hazards, ages 65--89, men, causes 41."
##
cap22 <- "Total hazard of dying before age 90 for a 60 year old person by HISCLASS and decade, women (top) and men (bottom), causes 41."
scap22 <- "Total hazard by HISCLASS, ages 65--89, causes 41."    
cap22log <- "Total hazard of dying before age 90 for a 60 year old person by HISCLASS and decade, women (top) and men (bottom). The last decades, causes 41."
scap22log <- "Total hazard by HISCLASS, ages 65--89, last years, causes 41."

<<41hazcalw>>=
source("R/getPHglm2.R")
resw <- getPHglm2(vb4064[vb4064$sex == "female", ],
            nper, labb)
resm <- getPHglm2(vb4064[vb4064$sex == "male", ],
            nper, labb)
@

<<41hazplotw, fig.cap = cap1w, fig.scap = scap1w, fig.height = 7>>=
source("R/plotHaz.glm.R")

<<41hazplotm, fig.cap = cap1m, fig.scap = scap1m, fig.height = 7>>=
plotHaz.glm(resm[-(1:6)], main = labb, col = scol, layout = c(2, 2))
@

<<41cumsw, fig.cap = cap12, fig.scap = scap12, fig.height = 10>>=
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
woutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "H(65|40)",
                main = "Women", exclude = 5:6)
moutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "H(65|40)",
                main = "Men", exclude = 5:6)
par(oldpar)
@

<<41cumslogw, fig.cap = cap12log, fig.scap = scap12log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw[-(1:6)], col = scol, logScale = FALSE, ylab = "H(65|40)",
main = "Women")
mloutp <- plotED.glm(resm[-(1:6)], col = scol, logScale = FALSE, ylab = "H(65|40)",
main = "Men")
par(oldpar)
@

<<41lissyoung>>=
library(eha)
library(xtable)
load("data/loTab.rda")
loTab$period <- factor(loTab$period)
liss4064 <- loTab[loTab$age < 64.5, ]
@

The statistical significance of the covariates are shown in Table~\ref{tab:liswom}
<<41liswom, results = 'asis'>>=
fitw1 <- glm(event ~ offset(log(exposure)) + as.factor(age) + urban + period + civst + income + educ, family = poisson, data = liss4064[liss4064$sex == "female", ])
##cat("Women:\n")
drw <- drop1(fitw1, test = "Chisq")
xtable(drw, caption = "Effect of covariates for women 40-64, 1990-2005, causes 41.", label = "tab:liswom")
##round(summary(fitw1)$coef[-(1:13), ], 4)
@

<<41liswomfig, fig.cap = "Effect sizes, women 40-64, 1990-2005, causes 41.", fig.height = 4>>=
source("R/plotWEduc.R")
plotWEduc(fitw1)
@

<<41lismen, results='asis'>>=
fitm1 <- glm(event ~ offset(log(exposure)) + as.factor(age) + urban + period + civst + income + educ, family = poisson, data = liss4064[liss4064$sex == "male", ])
##cat("\nMen:\n")
drm <- drop1(fitm1, test = "Chisq")
xtable(drm, caption = "Effect of covariates for men 40-64, 1990-2005, causes 41.")
##round(summary(fitm1)$coef[-(1:13), ], 4)
dcol <- c("blue", "darkgreen", "darkgreen", "red")
@

<<41lismanfig, fig.cap = "Effect sizes, men 40-64, 1990-2005, causes 41.", fig.height = 4>>=
#source("R/plotWEduc.R")
plotWEduc(fitm1)
@

<<41plotliss1, fig.cap = "Cumulative hazards, ages 40--64, 2002--2013, causes 41.", fig.height = 4>>=
#oldpar <- par(mfrow = c(1, 2))
#plot(fitw1, fn = "cum", col = dcol, main = "Women")
#plot(fitm1, fn = "cum", col = dcol, main = "Men")
#par(oldpar)
##summary(fitw1)
##summary(fitm1)
@

%See Table~\ref{tab:tablisswom1} the PH regression for women.
<<41tablisswom1, results = "asis">>=
#fitwo1 <- coxreg(Surv(enter, exit, event) ~ DISPINK + CIV + SUN2000NIVA, 
#                 data = liss4064[liss4064$sex == "female", ])
#dr <- drop1(fitwo1, test = "Chisq")
#ltx(fitwo1, dr = dr, caption = "PH regression, women aged 40--64, 2002--2013.", 
#    label = "tab:tablisswom1")
@

%See Table~\ref{tab:tablissman1} the PH regression for men.
<<41tablissman1, results = "asis">>=
#fitma1 <- coxreg(Surv(enter, exit, event) ~ DISPINK + CIV + SUN2000NIVA, 
#                 data = liss4064[liss4064$sex == "male", ])
#dr <- drop1(fitma1, test = "Chisq")
#ltx(fitma1, dr = dr, caption = "PH regression, men aged 40--64, 2002--2013.", 
 #   label = "tab:tablissman1")
@

%The distribution over time periods.
<<41getske6089>>=
vb6089 <- vbTab[as.numeric(as.character(vbTab$age)) >= 64.5, ]
vb6089$age <- factor(vb6089$age) # NOTE:: No change to '6589'!
@

<<41hazcalwold>>=
resw <- getPHglm(vb6089[vb6089$sex == "female", ],
              nper, labb)
resm <- getPHglm(vb6089[vb6089$sex == "male", ],
                nper, labb)
@

<<41hazplotwold, fig.cap = cap2w, fig.scap = scap2w, fig.height = 7>>=
##source("R/plotHaz.R")
plotHaz.glm(resw[-(1:6)], main = labb, layout = c(2, 2), col = scol)
@

<<41hazplotmold, fig.cap = cap2w, fig.scap = scap2m, fig.height = 7>>=
plotHaz.glm(resm[-(1:6)], main = labb, layout = c(2, 2), col = scol)
@

<<41cumswold, fig.cap = cap22, fig.scap = scap22, fig.height = 10>>=
##source("R/plotED.R")
oldpar <- par(mfrow = c(2, 1))
woutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "H(90|65)",
                main = "Women", exclude = 5:6)
moutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "H(90|65)",
                main = "Men", exclude = 5:6)
par(oldpar)
@

<<41cumslogwm, fig.cap = cap22log, fig.scap = scap22log, fig.height = 10>>=
oldpar <- par(mfrow = c(2, 1))
wloutp <- plotED.glm(resw[-(1:6)], col = scol, logScale = FALSE, ylab = "H(90|65)",
main = "Women")
mloutp <- plotED.glm(resm[-(1:6)], col = scol, logScale = FALSE, ylab = "H(90|65)",
main = "Men")
par(oldpar)
@

<<41lissyoung2>>=
library(eha)
library(xtable)
##load("data/loTab.rda")
##loTab$period <- factor(loTab$period)
liss6589 <- loTab[loTab$age > 64.5, ]
@

The statistical significance of the covariates are shown in Table~\ref{tab:liswom}
<<41liswom2, results = 'asis'>>=
fitw2 <- glm(event ~ offset(log(exposure)) + as.factor(age) + urban + period + civst + income + educ, family = poisson, data = liss6589[liss6589$sex == "female", ])
##cat("Women:\n")
drw2 <- drop1(fitw2, test = "Chisq")
xtable(drw2, caption = "Effect of covariates for women 65-89, 1990-2005, causes 41.", label = "tab:liswom")
##round(summary(fitw1)$coef[-(1:13), ], 4)
@

<<41liswomfig2, fig.cap = "Effect sizes, women 65-89, 1990-2005, causes 41.", fig.height = 4>>=
#source("R/plotWEduc.R")
plotWEduc(fitw2)
@

<<41lismen2, results='asis'>>=
fitm2 <- glm(event ~ offset(log(exposure)) + as.factor(age) + urban + period + civst + income + educ, family = poisson, data = liss6589[liss6589$sex == "male", ])
##cat("\nMen:\n")
drm2 <- drop1(fitm2, test = "Chisq")
xtable(drm2, caption = "Effect of covariates for men 65-89, 1990-2005, causes 41.")
##round(summary(fitm1)$coef[-(1:13), ], 4)
dcol <- c("blue", "darkgreen", "darkgreen", "red")
@

<<41lismanfig2, fig.cap = "Effect sizes, men 65-89, 1990-2005, causes 41.", fig.height = 4>>=
#source("R/plotWEduc.R")
plotWEduc(fitm2)
@
